---
title: "General Demographics Functions"
output: github_document
---

```{r, comment=NA, echo=FALSE}
tools::Rd2txt_options(underline_titles=FALSE)
```

# General Demographics Dashboard Functions

## Wrangling Functions

### wrangle_general 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/wrangle_general.Rd")
```

### obtain_raw_general_data 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/obtain_raw_general_data.Rd")
```

### obtain_language_info 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/obtain_language_info.Rd")
```

### obtain_country_info 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/obtain_country_info.Rd")
```

### prepare_general_data 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/prepare_general_data.Rd")
```

### write_general_data 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/write_general_data.Rd")
```

## Server Functions

### convert_loe 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/convert_loe.Rd")
```

### get_loe_df 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/get_loe_df.Rd")
```

### get_loe_plot 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/get_loe_plot.Rd")
```

### get_age_df 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/get_age_df.Rd")
```

### get_age_plot 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/get_age_plot.Rd")
```

### get_top_country_df 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/get_top_country_df.Rd")
```

### get_country_plot 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/get_country_plot.Rd")
```

### get_top_language_df 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/get_top_language_df.Rd")
```

### get_language_plot 
#### Main Documentation
```{r, comment=NA, echo=FALSE}
tools::Rd2txt("../../r-package/man/get_language_plot.Rd")
```