---
title: "R functions for wrangling and serving the link or page related data"
output: github_document
---

# Link and Page Dashboard Functions

## Wrangling Functions

```{r, comment=NA, echo=FALSE}
tools::Rd2txt_options(underline_titles=FALSE)
root <- "../../r-package/man/"
ext <- ".Rd"
```


### read_course_axis

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "read_course_axis", ext))
```


### read_link_dirt

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "read_link_dirt", ext))
```


### hash_username

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "hash_username", ext))
```


### set_activity_level

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "set_activity_level", ext))
```


### get_module_of_link

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_module_of_link", ext))
```

### write_link_clean 

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "write_link_clean", ext))
```

### read_page_dirt

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "read_page_dirt", ext))
```


### prepare_tidy_page

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "prepare_tidy_page", ext))
```


### prepare_page_name

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "prepare_page_name", ext))
```

### write_page_clean 

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "write_page_clean", ext))
```

### wrangle_link_page

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "wrangle_link_page", ext))
```


## Server Functions


### filter_chapter_linkpage

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "filter_chapter_linkpage", ext))
```


### get_pageview 

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_pageview", ext))
```


### get_page_name  

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_page_name", ext))
```


### get_unique_page_name

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_unique_page_name", ext))
```


### creat_page_table

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "creat_page_table", ext))
```


### get_click_per_link

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_click_per_link", ext))
```

### creat_link_table

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "creat_link_table", ext))
```
