---
title: "R functions for wrangling and serving the discussion forum data"
output: github_document
---

# Discussion Forum Dashboard Functions

## Wrangling Functions

```{r, comment=NA, echo=FALSE}
tools::Rd2txt_options(underline_titles=FALSE)
root <- "../../r-package/man/"
ext <- ".Rd"
```


### get_activity_levels

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_activity_levels", ext))
```



### get_discussion_vars_json

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_discussion_vars_json", ext))
```



### get_discussion_vars_xml

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_discussion_vars_xml", ext))
```



### infer_post_subcategories

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "infer_post_subcategories", ext))
```



### prepare_json

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "prepare_json", ext))
```



### prepare_posts

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "prepare_posts", ext))
```



### prepare_searches

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "prepare_searches", ext))
```



### prepare_views

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "prepare_views", ext))
```



### prepare_words

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "prepare_words", ext))
```



### prepare_xml

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "prepare_xml", ext))
```



### wrangle_forum

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "wrangle_forum", ext))
```



## Server Functions

### apply_forum_filters

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "apply_forum_filters", ext))
```




### calculate_forum_searches

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "calculate_forum_searches", ext))
```




### count_authors

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "count_authors", ext))
```




### count_posts

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "count_posts", ext))
```




### count_views

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "count_views", ext))
```




### filter_forum_elements

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "filter_forum_elements", ext))
```




### filter_wordcloud_data

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "filter_wordcloud_data", ext))
```




### gather_post_types

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "gather_post_types", ext))
```




### get_author_count

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_author_count", ext))
```




### get_forum_threads

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_forum_threads", ext))
```




### get_label_lengths

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_label_lengths", ext))
```




### get_post_types

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_post_types", ext))
```




### get_subcategory_options

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_subcategory_options", ext))
```




### get_target_word_counts

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_target_word_counts", ext))
```




### get_wordcloud_data

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_wordcloud_data", ext))
```




### make_forum_barplot

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "make_forum_barplot", ext))
```




### make_forum_breakdown_barplot

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "make_forum_breakdown_barplot", ext))
```




### make_wordcloud

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "make_wordcloud", ext))
```




### set_axis_limit

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "set_axis_limit", ext))
```




### set_breakdown

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "set_breakdown", ext))
```




### set_forum_plot_title

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "set_forum_plot_title", ext))
```




### set_forum_plot_ylabel

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "set_forum_plot_ylabel", ext))
```




### set_forum_threads_title

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "set_forum_threads_title", ext))
```




### set_wordcloud_title

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "set_wordcloud_title", ext))
```




### specify_forum_data_selection

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "specify_forum_data_selection", ext))
```




### update_forum_data

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "update_forum_data", ext))
```


