---
title: "R functions for wrangling and serving the discussion problem data"
output: github_document
---

# Problem Dashboard Functions

## Assessment Functions

```{r, comment=NA, echo=FALSE}
tools::Rd2txt_options(underline_titles=FALSE)
root <- "../../r-package/man/"
ext <- ".Rd"
```


### extract_assessment_json

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "extract_assessment_json", ext))
```

### extract_assessment_csv

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "extract_assessment_csv", ext))
```

### join_extracted_assessment_data

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "join_extracted_assessment_data", ext))
```

### summarise_joined_assessment_data

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "summarise_joined_assessment_data", ext))
```

### plot_assessment

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "plot_assessment", ext))
```

## Problems Functions

### clean_multiple_choice

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "clean_multiple_choice", ext))
```

### create_question_lookup_from_json

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "create_question_lookup_from_json", ext))
```

### filter_valid_questions

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "filter_valid_questions", ext))
```

### get_mean_scores

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_mean_scores", ext))
```

### tally_correct_answers

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "tally_correct_answers", ext))
```

### calculate_percent_correct_tbl

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "calculate_percent_correct_tbl", ext))
```

### get_mean_scores_filterable

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_mean_scores_filterable", ext))
```

### join_summary_lookup

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "join_summary_lookup", ext))
```

### summarise_scores_by_chapter

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "summarise_scores_by_chapter", ext))
```

### prepare_filterable_problems

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "prepare_filterable_problems", ext))
```

### get_extreme_summarised_scores

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "get_extreme_summarised_scores", ext))
```

### join_problems_to_lookup

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "join_problems_to_lookup", ext))
```

### join_users_problems

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "join_users_problems", ext))
```

### filter_counts

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "filter_counts", ext))
```

### filter_extreme_problem_choices

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "filter_extreme_problem_choices", ext))
```

### aggregate_extracted_problems

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "aggregate_extracted_problems", ext))
```

### aggregate_melted_problems

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "aggregate_melted_problems", ext))
```

### plot_aggregated_problems

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "plot_aggregated_problems", ext))
```

### plot_problem_chapter_summaries

#### Main Documentation

```{r, comment=NA, echo=FALSE}
tools::Rd2txt(paste0(root, "plot_problem_chapter_summaries", ext))
```



